**The Place of Interoception and Theory of Mind in Deception**

### 2021-11-11 3_ToM.Rmd
add significance stars to plots

```{r message=FALSE, warning=FALSE}
plot_effect <- function(model, var = "YONI_Total", outcome = "Confidence") {
  data <- df |> 
    group_by(Participant, Answer, Condition) |> 
    summarise({{var}} := mean(.data[[var]], na.rm = TRUE),
              SD = sd(.data[[outcome]], na.rm = TRUE),
              {{outcome}} := mean(.data[[outcome]], na.rm = TRUE),
              CI_low = .data[[outcome]] - SD / 2,
              CI_high = .data[[outcome]] + SD / 2)

  dodge_width <- 0.02 * diff(range(data[[var]]))
  ylab <- ifelse(outcome == "RT", "Reaction Time (s)", "Confidence")

  link_data <- estimate_relation(model, at = c("Condition", var, "Answer"), length = 30)
  ggplot(link_data, aes_string(x = var, y = "Predicted")) +
    geom_pointrange(data = data, aes_string(y = outcome, color = "Condition", ymin = "CI_low", ymax = "CI_high"), position = position_dodge(width = dodge_width)) +
    geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 0.33) + 
    geom_line(aes(color = Condition)) +
    labs(y = ylab, x = paste0(stringr::str_replace(var, "_", " ("), ")")) +
    scale_color_manual(values = c("Polygraph" = "#FF5722", "Social" = "#2196F3")) +
    scale_fill_manual(values = c("Polygraph" = "#FF5722", "Social" = "#2196F3")) +
    facet_wrap(~Answer) 
}

p_conf_yoni_total <- plot_effect(model, var = "YONI_Total", outcome = "Confidence")
# p_conf_yoni_total
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_yoni_total <- plot_effect(model, var = "YONI_Total", outcome = "RT")
# p_rt_yoni_total
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_yoni_cognitive <- plot_effect(model, var = "YONI_Cognitive", outcome = "Confidence")
# p_conf_yoni_cognitive
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_yoni_cognitive <- plot_effect(model, var = "YONI_Cognitive", outcome = "RT")
# p_rt_yoni_cognitive
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_yoni_affective <- plot_effect(model, var = "YONI_Affective", outcome = "Confidence")
# p_conf_yoni_affective
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_yoni_affective <- plot_effect(model, var = "YONI_Affective", outcome = "RT")
# p_rt_yoni_affective
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_yoni_physical <- plot_effect(model, var = "YONI_Physical", outcome = "Confidence")
# p_conf_yoni_physical
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_yoni_physical <- plot_effect(model, var = "YONI_Physical", outcome = "RT")
# p_rt_yoni_physical
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_bes_total <- plot_effect(model, var = "BES_Total", outcome = "Confidence")
# p_conf_bes_total
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_bes_total <- plot_effect(model, var = "BES_Total", outcome = "RT")
# p_rt_bes_total
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_bes_cognitive <- plot_effect(model, var = "BES_Cognitive", outcome = "Confidence")
# p_conf_bes_cognitive
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_bes_cognitive <- plot_effect(model, var = "BES_Cognitive", outcome = "RT")
# p_rt_bes_cognitive
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_bes_affective <- plot_effect(model, var = "BES_Affective", outcome = "Confidence")
# p_conf_bes_affective
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_bes_affective <- plot_effect(model, var = "BES_Affective", outcome = "RT")
# p_rt_bes_affective
```

@@

```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
r <- get_correlation(var = "BES_")
r$plot
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_bes_total / 
  p_conf_bes_cognitive / 
  p_conf_bes_affective +
  patchwork::plot_annotation(title = "Empathy", theme = theme(plot.title = element_text(hjust = 0.5)))

>>>>

```{r message=FALSE, warning=FALSE}
plot_effect <- function(model, results, var = "YONI_Total", outcome = "Confidence") {
  data <- df |> 
    group_by(Participant, Answer, Condition) |> 
    summarise({{var}} := mean(.data[[var]], na.rm = TRUE),
              SD = sd(.data[[outcome]], na.rm = TRUE),
              {{outcome}} := mean(.data[[outcome]], na.rm = TRUE),
              CI_low = .data[[outcome]] - SD / 2,
              CI_high = .data[[outcome]] + SD / 2)

  link_data <- estimate_relation(model, at = c("Condition", var, "Answer"), length = 30)
  range_x <- diff(range(data[[var]]))

  annot <- results$marginal_effects  
  annot$Label <- insight::format_p(annot$p, stars_only = TRUE)
  annot$x <- mean(range(data[[var]]))
  annot$x <- ifelse(annot$Condition == "Polygraph", 
                    annot$x - 0.05 * range_x, 
                    annot$x + 0.05 * range_x)
  annot$y <- max(data[[outcome]]) - 0.01 * diff(range(data[[outcome]]))

  p <- ggplot(link_data, aes_string(x = var, y = "Predicted")) +
    geom_pointrange(data = data, 
                    aes_string(y = outcome, 
                               color = "Condition", 
                               ymin = "CI_low", 
                               ymax = "CI_high"), 
                    position = position_dodge(width = 0.02 * range_x)) +
    geom_ribbon(aes(ymin = CI_low, ymax = CI_high, fill = Condition), alpha = 0.33) + 
    geom_line(aes(color = Condition)) +
    geom_text(data=annot, aes(x = x, y = y, label = Label, color = Condition), 
              size = 8, show.legend = FALSE) +
    labs(y = ifelse(outcome == "RT", "Reaction Time (s)", "Confidence"), 
         x = paste0(stringr::str_replace(var, "_", " ("), ")")) +
    scale_color_manual(values = c("Polygraph" = "#FF5722", "Social" = "#2196F3")) +
    scale_fill_manual(values = c("Polygraph" = "#FF5722", "Social" = "#2196F3")) + 
    facet_wrap(~Answer)

  # Narrow y range
  if(outcome == "Confidence") {
    p <- p +
      coord_cartesian(ylim = c(0, 1)) +
      scale_y_continuous(expand=expansion(c(0, 0))) 
  }
  p
}

p_conf_yoni_total <- plot_effect(model, results, var = "YONI_Total", outcome = "Confidence")
# p_conf_yoni_total
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_yoni_total <- plot_effect(model, results, var = "YONI_Total", outcome = "RT")
# p_rt_yoni_total
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_yoni_cognitive <- plot_effect(model, results, var = "YONI_Cognitive", outcome = "Confidence")
# p_conf_yoni_cognitive
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_yoni_cognitive <- plot_effect(model, results, var = "YONI_Cognitive", outcome = "RT")
# p_rt_yoni_cognitive
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_yoni_affective <- plot_effect(model, results, var = "YONI_Affective", outcome = "Confidence")
# p_conf_yoni_affective
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_yoni_affective <- plot_effect(model, results, var = "YONI_Affective", outcome = "RT")
# p_rt_yoni_affective
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_yoni_physical <- plot_effect(model, results, var = "YONI_Physical", outcome = "Confidence")
# p_conf_yoni_physical
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_yoni_physical <- plot_effect(model, results, var = "YONI_Physical", outcome = "RT")
# p_rt_yoni_physical
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_bes_total <- plot_effect(model, results, var = "BES_Total", outcome = "Confidence")
# p_conf_bes_total
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_bes_total <- plot_effect(model, results, var = "BES_Total", outcome = "RT")
# p_rt_bes_total
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_bes_cognitive <- plot_effect(model, results, var = "BES_Cognitive", outcome = "Confidence")
# p_conf_bes_cognitive
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_bes_cognitive <- plot_effect(model, results, var = "BES_Cognitive", outcome = "RT")
# p_rt_bes_cognitive
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_bes_affective <- plot_effect(model, results, var = "BES_Affective", outcome = "Confidence")
# p_conf_bes_affective
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_bes_affective <- plot_effect(model, results, var = "BES_Affective", outcome = "RT")
# p_rt_bes_affective
```

@@

```{r message=FALSE, warning=FALSE}
r <- get_correlation(var = "BES_")
r$plot
```

@@

```{r message=FALSE, warning=FALSE, fig.height=figheight*3, fig.width=figwidth*1.5}
p_conf_bes_total / 
  p_conf_bes_cognitive / 
  p_conf_bes_affective +
  patchwork::plot_annotation(title = "Empathy", theme = theme(plot.title = element_text(hjust = 0.5)))

### 2021-11-11 4_Intero.Rmd
add significance stars to plots

```{r message=FALSE, warning=FALSE}
p_conf_hct_accuracy <- plot_effect(model, var = "HCT_Accuracy", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_hct_accuracy <- plot_effect(model, var = "HCT_Accuracy", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_hct_confidence <- plot_effect(model, var = "HCT_Confidence", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_hct_confidence <- plot_effect(model, var = "HCT_Confidence", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_hct_awareness <- plot_effect(model, var = "HCT_Awareness", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_hct_awareness <- plot_effect(model, var = "HCT_Awareness", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_maia_total <- plot_effect(model, var = "MAIA_Total", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_maia_total <- plot_effect(model, var = "MAIA_Total", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_maia_noticing <- plot_effect(model, var = "MAIA_Noticing", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_maia_noticing <- plot_effect(model, var = "MAIA_Noticing", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_maia_notdistracting <- plot_effect(model, var = "MAIA_NotDistracting", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_maia_notdistracting <- plot_effect(model, var = "MAIA_NotDistracting", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_maia_bodylistening <- plot_effect(model, var = "MAIA_BodyListening", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_maia_bodylistening <- plot_effect(model, var = "MAIA_BodyListening", outcome = "RT")
```

>>>>

```{r message=FALSE, warning=FALSE}
p_conf_hct_accuracy <- plot_effect(model, results, var = "HCT_Accuracy", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_hct_accuracy <- plot_effect(model, results, var = "HCT_Accuracy", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_hct_confidence <- plot_effect(model, results, var = "HCT_Confidence", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_hct_confidence <- plot_effect(model, results, var = "HCT_Confidence", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_hct_awareness <- plot_effect(model, results, var = "HCT_Awareness", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_hct_awareness <- plot_effect(model, results, var = "HCT_Awareness", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_maia_total <- plot_effect(model, results, var = "MAIA_Total", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_maia_total <- plot_effect(model, results, var = "MAIA_Total", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_maia_noticing <- plot_effect(model, results, var = "MAIA_Noticing", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_maia_noticing <- plot_effect(model, results, var = "MAIA_Noticing", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_maia_notdistracting <- plot_effect(model, results, var = "MAIA_NotDistracting", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_maia_notdistracting <- plot_effect(model, results, var = "MAIA_NotDistracting", outcome = "RT")
```

@@

```{r message=FALSE, warning=FALSE}
p_conf_maia_bodylistening <- plot_effect(model, results, var = "MAIA_BodyListening", outcome = "Confidence")
```

@@

```{r message=FALSE, warning=FALSE}
p_rt_maia_bodylistening <- plot_effect(model, results, var = "MAIA_BodyListening", outcome = "RT")
```
